Generating Simulated Data

### 2021-04-09 docs/SimData.Rmd
binwidth function dev

binwidths <- function(Lmin, Lmax, vonBk, Nsizebins){
  #optimal bin size is lower end
  binopt <- 0.23*Lmax^0.6
  #vonBk tells you how many fine bins for fast growth
  #low vonBK is doesn't asympote, divide length range equally into nbins?

>>>>

binwidths <- function(Lmin, Lmax, vonBk, Nsizebins){
  #optimal bin size is lower end
  binopt <- 0.23*Lmax^0.6

  #range gives initial default binwidth, all equal (range/Nbins)
  bindef <- (Lmax-Lmin)/Nsizebins

  #vonBk tells you how many fine bins for fast growth
  # threshold cumprod of 0.05 to define last bin? tiny growth increment
  # use binopt up to this threshold?
  # plot(cumprod(rep(1, 160)*exp(-0.0386)), ylim=c(0,1), xlim=c(0,180)) #saithe
  # lines(cumprod(rep(1, 20)*exp(-1.4)), ylim=c(0,1), xlim=c(0,180)) #capelin
  # lines(cumprod(rep(1, 40)*exp(-0.163)), ylim=c(0,1), xlim=c(0,180)) #redfish
  # lines(cumprod(rep(1, 130)*exp(-0.344)), ylim=c(0,1), xlim=c(0,180)) #cod
  #low vonBK is doesn't asympote, divide length range equally into nbins?
